---
title: "Descriptive analysis (imputed)"
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Load packages 

```{r}
if (!require(pacman)) install.packages("pacman")

pacman::p_load(tidyverse, # tidyverse 
               panelr, # panel data analysis
               here, # computational reproducibility 
               glue, # gluing objects and strings 
               tidylog, # logging analysis
               naniar, # missing data 
               zeallot, # multiple assignments 
               readxl, 
               ggpubr,
               hrbrthemes, 
               broom, 
               jtools, 
               patchwork, 
               glmer, 
               broom.mixed, 
               estimatr, 
               stargazer,
               DeclareDesign,
               sensemakr,
               mice,
               usmap,
               janitor,
               modelsummary)

source(here("functions/utils.r"))
```

# Load files 

```{r message = FALSE}
df <- read.csv(here("processed_data", "panel_data_cleaned.csv"))
```

# Summary statistics 

```{r}
data("state")
for (i in 1:50) {

  df$state[df$state == i] <- state.abb[i]

}

state_tab <- janitor::tabyl(df$state) %>%
  tibble()

# Quick fixing 
names(state_tab)[1] <- "state"
state_tab$percent <- state_tab$percent*100

state_tab %>%
  arrange(desc(percent)) %>%
  head(10)

# Plotting 
state_map <- plot_usmap(data = state_tab, 
           values = "percent",
           color = "red",
           labels = TRUE,
           label_color = "blue",
           alpha = 0.25) +
  scale_fill_continuous(
    low = "white", high = "red",
    name = "Percentage") + 
  theme(legend.position = "right") +
  labs(title = "Spatial distribution of respondents")

png(filename = here("outputs", "states.png"), 
    res = 72)
state_map
dev.off()

df$yearborn <- ifelse(df$yearborn > 2021 | df$yearborn < 1900, NA, df$yearborn)

df$age_non_scale <- 2021 - df$yearborn

subset_df <- df %>% select(usborn, DEM, GOP, age_non_scale, male, edu)

datasummary(All(subset_df) ~ Mean,
            data = subset_df)
```

# Summarize by group 

```{r}
var.list <- NULL
var.list <- names(df)[str_detect(names(df), "disc")][c(1, 3)]

var.list <- c(var.list, c("linkedfate", "idimport", "asnpride", "rona.behav.sneeze", "rona.behav.language", "rona.behav.walk", "rona.behav.transit", "rona.behav.other", "rona.behav.nochange", "rona.index", "X2020likelyvote", "biden", "DEM", "DEM.strong", "GOP", "GOP.strong", "unfair", "ronaunfairasian", "apa.responsible", "apa.have.rona", "apa.harassment", "unfair_others", "whiteaffect", "blackaffect", "latinoaffect", "asianaffect"))
```

```{r message = FALSE}
group_sum <- purrr::map_dfr(seq(var.list), group_mean) %>%
    mutate(variable = rep(var.list, each = 3)) %>%
    filter(!is.na(mean)) 
```

## Discrimination perception 

```{r}
group_sum %>%
    filter(str_detect(variable, "disc")) %>%
    mutate(variable = recode(variable, 
                             "apa.discrim.rona" = "COVID-19 discrimination",
                             "gendiscrim" = 
                                 "General discrimination")) %>%
    ggplot(aes(x = factor(wave_fac), y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low)) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = round(mean, 2))) +
        facet_wrap(~variable) +
        labs(title = "Changes in discrimination perception",
            x = "", y = "Average response") +
        geom_hline(yintercept = 0.5,  linetype = 'dotted', col = 'red', size = 1)

ggsave(here("outputs", "disc.perception_imputed.png"))
```

```{r}
gen_density <- df %>%
  ggplot(aes(gendiscrim)) +
    geom_density() +
    facet_wrap(~wave_fac) +
    labs(x = "Response",
         y = "Density",
         title = "General discrimination") +
    geom_vline(xintercept = 0.5,  linetype = 'dotted', col = 'red', size = 1)

rona_density <- df %>%
  ggplot(aes(apa.discrim.rona)) +
    geom_density() +
    facet_wrap(~wave_fac) +
    labs(x = "Response",
         y = "Density",
         title = "COVID-19 discrimination") +
    geom_vline(xintercept = 0.5,  linetype = 'dotted', col = 'red', size = 1)

(gen_density / rona_density) + plot_annotation(tag_levels = "A")

ggsave(here("outputs", "density.png"), width = 10)
```


## Affect 

```{r}
group_sum %>%
  filter(wave_fac != "November") %>% 
  filter(str_detect(variable, "affect")) %>%
  mutate(variable = recode(variable, 
                           "asianaffect" = "Asian",
                           "latinoaffect" = "Latino",
                           "blackaffect" = "Black",
                           "whiteaffect" = "White")) %>%
  mutate(mean = round(mean, 2)) %>%
  ggplot(aes(x = wave_fac, y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low,
             col = variable)) +
        geom_pointrange() +
        labs(x = "", y = "Average response",
            col = "Affect") +
        geom_hline(yintercept = 3.5, linetype = 'dotted', col = 'red', size = 1) +
        scale_colour_brewer(palette = "Set1")

ggsave(here("outputs", "affect.png"))
```

```{r}
group_sum %>%
    filter(wave_fac == "May") %>% 
    filter(str_detect(variable, "rona")) %>%
    filter(!str_detect(variable, "apa|nochange|2020|biden|DEM|GOP|fair|affect")) %>%
    mutate(variable = recode(variable, 
                             "rona.behav.sneeze" = "Avoid coughing/sneezing",
                             "rona.behav.language" = 
                             "Avoid speaking Asian language",
                             "rona.behav.walk" = "Avoid walking in neighborhoods",
                             "rona.behav.transit" = "Avoid public transporation",
                             "rona.behav.other" = "Others",
                             "rona.index" = "Average response")) %>%
  mutate(mean = mean*100) %>%
    ggplot(aes(x = factor(variable), y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low)) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = paste0(round(mean, 2), "%"))) +
        labs(title = "COVID-19 related marginalized experience (Wave 2)",
            x = "", y = "Percentage") +
        coord_flip() +
        scale_y_continuous(labels = ~paste0(., "%"))

ggsave(here("outputs", "rona_behave.png"), width = 10)
```

```{r}
group_sum %>%
    #filter(wave_fac == "May") %>% 
    filter(str_detect(variable, "fair|treat")) %>%
    mutate(variable = recode(variable, 
 "ronaunfairasian" = "Experienced COVID discrimination due to race",
 "unfair" = "Experienced COVID-19 discrimination",
 "unfair_others" = "Witnessed COVID discrimination")) %>%
  mutate(mean = mean*100) %>%
    ggplot(aes(x = wave_fac, y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low)) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = paste0(round(mean, 2), "%"))) +
        labs(title = "COVID-19 related unfair treatment",
            x = "", y = "Percentage") +
        facet_wrap(~variable) +
        scale_y_continuous(labels = ~paste0(., "%"))

ggsave(here("outputs", "rona_fair.png"), width = 12)
```

```{r}
summary(lm(df$apa.discrim.rona ~ df$unfair_others))
```

```{r}
# Lost job 
lost_job_pct <- sum(!is.na(df %>%
  filter(wave == 2) %>% 
  pull(lostjob)))/(df %>% filter(wave == 2) %>% nrow()) %>%
  round(2)
```

5% participants in the wave 2 lost jobs. 

```{r}
income_reduction_pct <- sum(!is.na(df %>%
  filter(wave == 2) %>% 
  pull(incomereduc)))/(df %>% filter(wave == 2) %>% nrow()) %>%
  round(2)

income_reduction_pct
```

```{r}
df$lostjob <- if_else(!is.na(df$lostjob), 1, 0)
df$incomereduc <- if_else(!is.na(df$incomereduc), 1, 0)

summary(lm(unfair ~ lostjob + incomereduc, data = subset(df, wave == 2)))

summary(lm(unfair_others ~ lostjob + incomereduc, data = subset(df, wave == 2)))

summary(lm(apa.discrim.rona ~ lostjob + incomereduc, data = subset(df, wave == 2)))
```

2% participants in the wave experienced income reduction.

```{r}
df$testrona <- if_else(df$testrona == 1, 1, 0)
  
test_rona_pct <- df %>%
  filter(wave != 1) %>%
  summarize(mean = mean(testrona, na.rm = T))

test_rona_pct$mean
```

7% of participants tested positive 

```{r}
df %>%
  group_by(wave) %>%
  summarize(rona_pos = mean(testrona, na.rm = TRUE))
```

```{r}
pol_bev_plot <- group_sum %>%
    filter(str_detect(variable, "2020|biden")) %>%
    filter(wave_fac != "February") %>%
    mutate(variable = recode(variable, 
                             "biden" = "Supporting Biden candidacy",
                             "X2020likelyvote" = "Will vote in 2020 election")) %>%
    ggplot(aes(x = factor(wave_fac), y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low)) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = paste0(round(mean, 2)*100, "%"))) +
        scale_y_continuous(labels = scales::percent) +
        facet_wrap(~variable) +
        labs(title = "Changes in political preferences",
            x = "", y = "") 

pol_bev_plot
ggsave(here("outputs", "political_outcome.png"))
```

```{r}
pid_plot <- group_sum %>%
    filter(str_detect(variable, "GOP|DEM")) %>%
    filter(!str_detect(variable, "strong")) %>%
    mutate(variable = recode(variable, 
                             "biden" = "Supporting Biden candidacy",
                             "X2020likelyvote" = "Will vote in 2020 election")) %>%
    ggplot(aes(x = factor(wave_fac), y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low)) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = paste0(round(mean, 2)*100, "%"))) +
        scale_y_continuous(labels = scales::percent) +
        facet_wrap(~variable) +
        labs(title = "Changes in party identification",
            x = "Wave", y = "Percentage")

pid_plot
ggsave(here("outputs", "pid.png"))

(pol_bev_plot + pid_plot) + plot_annotation(tag_levels = "A")

ggsave(here("outputs", "pol_bev.png"), width = 10)
```

## General and COVID-19 discrimination perception

```{r}
df$proxy <- rep(subset(df, wave == 1)$gendiscrim, 3)

plot_w12 <- df %>%
    filter(wave %in% c(1,2)) %>%
    group_by(proxy) %>%
    summarise(mean = mean(apa.discrim.rona, na.rm = TRUE),
                  ci_high = ci.high(apa.discrim.rona),
                  ci_low = ci.low(apa.discrim.rona)) %>%
    mutate(group = 2)

plot_w13 <- df %>%
    filter(wave %in% c(1,3)) %>%
    group_by(proxy) %>%
    summarise(mean = mean(apa.discrim.rona, na.rm = TRUE),
                  ci_high = ci.high(apa.discrim.rona),
                  ci_low = ci.low(apa.discrim.rona)) %>%
    mutate(group = 3)

plot_w123 <- bind_rows(plot_w12, plot_w13)
```

```{r}
plot_w123 %>%
    ggplot(aes(x = factor(proxy), y = mean,
               ymax = mean + ci_high, 
               ymin = mean - ci_low, 
               col = factor(group))) +
        geom_pointrange() +
        ggrepel::geom_text_repel(aes(label = round(mean, 2))) +
        labs(x = "Response to general discrimination Q in Wave 1", 
             y = "Average response to COVID-19 discrimination Q in Wave 2 and 3",
             col = "Wave") +
        geom_hline(yintercept = 0.5,  linetype = 'dotted', col = 'red', size = 1) +
        scale_colour_brewer(palette = "Set1")

ggsave(here("outputs", "disc.wave.png"), height = 9, width = 9)
```

```{r}
exp_plot <- df %>%
  filter(wave != 1) %>%
  group_by(proxy, wave) %>%
  summarize(mean = mean(unfair, na.rm = TRUE),
            ci_high = ci.high(unfair, na.rm = TRUE),
            ci_low = ci.low(unfair, na.rm = TRUE)) %>%
  ggplot(aes(x = proxy, y = mean, col = factor(wave),
             ymax = mean + ci_high,
             ymin = mean - ci_low)) +
    geom_pointrange() +
    ylim(c(0, 1)) +
    ggrepel::geom_text_repel(aes(label = round(mean, 2))) +
    labs(x = "Response to general discrimination Q in Wave 1", 
         y = "Average response",
         col = "Wave",
         title = "Experiencing COVID-19 discrimination") +
    scale_colour_brewer(palette = "Set1")

wit_plot <- df %>%
  filter(wave != 1) %>%
  group_by(proxy, wave) %>%
  summarize(mean = mean(unfair_others, na.rm = TRUE),
            ci_high  = ci.high(unfair_others, na.rm = TRUE),
            ci_low = ci.low(unfair_others, na.rm = TRUE)) %>%
  ggplot(aes(x = proxy, y = mean, col = factor(wave),
             ymax = mean + ci_high,
             ymin = mean - ci_low)) +
    geom_pointrange() +
    ylim(c(0, 1)) +
    ggrepel::geom_text_repel(aes(label = round(mean, 2))) +
    labs(x = "Response to general discrimination Q in Wave 1", 
         y = "Average response",
         col = "Wave",
         title = "Witnessing COVID-19 discrimination") +
    scale_colour_brewer(palette = "Set1")

(exp_plot / wit_plot) + plot_annotation(tag_levels = "A")

ggsave(here("outputs", "disc_exp_wit.png"), height = 12, width = 9)
```
# Regression analysis

## Imputation

```{r}
df_na_sum <- df %>%
  filter(wave != 1) %>%
  select(gendiscrim, apa.discrim.rona, usborn, DEM, GOP, age, male, edu, income) %>%
  map_dfr(~is.na(.) %>% mean())

df_na_sum
```

```{r}
imp <- mice(
  df %>%
    filter(wave != 1) %>%
    select(apa.discrim.rona, usborn, DEM, GOP, age, male, edu),
    seed = 1234, # for reproducibility
    m = 5, # the number of imputations
    maxit = 10, # the max number of iterations 
    method = "pmm", # predictive mean method
    print = FALSE)

densityplot(imp, layout = c(1,2))

imputed <- mice::complete(imp)

# Replace with the imputed values 
df$apa.discrim.rona[665:nrow(df)] <- 
imputed$apa.discrim.rona

df$DEM[665:nrow(df)] <- 
imputed$DEM

df$GOP[665:nrow(df)] <- 
imputed$GOP

df$age[665:nrow(df)] <- 
imputed$age
```

## Likely to vote 

```{r}
df$prior <- if_else(df$proxy <= 0.5 , 1, 0)

two.group <- bind_rows(tidy_test(usborn) %>% mutate(variable = "Born in US"),
  tidy_test(age) %>% mutate(variable = "Age"),
  tidy_test(male) %>% mutate(variable = "Male"),
  tidy_test(edu) %>% mutate(variable = "Education"),
  tidy_test(GOP) %>% mutate(variable = "Republican"),
  tidy_test(DEM) %>% mutate(variable = "Democrat")
) 

two.group %>%
  ggplot(aes(x = variable, y = estimate, 
             ymax = conf.high,
             ymin = conf.low)) +
    geom_pointrange() +
    geom_hline(yintercept = 0, linetype = "dotted", color = "red", size = 1) +
    labs(x = "",
         y = "Estimate")
  
ggsave(here("outputs", "estimate.two.group_imputed.png"), width = 8)

two.group %>%
  ggplot(aes(x = variable, y = p.value)) +
    geom_point() +
    geom_hline(yintercept = 0.05, linetype = "dotted", color = "red", size = 1) +
    labs(x = "",
         y = "P value")
  
ggsave(here("outputs", "p.value.two.group_imputed.png"), width = 8)

```

```{r}
model.outs <- cal_model_outputs(df)
model.outs.low <- cal_model_outputs(df %>%
                                      filter(prior == 1))
model.outs.high <- cal_model_outputs(df %>%
                                      filter(prior != 1))
```

### Main 

```{r}
model.outs %>%
  filter(!str_detect(term, "(Intercept)|sd")) %>%
  mutate(term = recode(term, 
                       "usborn" = "Born in US",
                       "male" = "Male",
                       "gendiscrim" = "General discrimination",
                       "apa.discrim.rona" = "COVID discrimination",
                       "edu" = "Education",
                       "factor(wave)3" = "Wave 3",
                       "GOP" = "Republican",
                       "DEM" = "Democrat",
                       "age" = "Age",
                       "income" = "Income")) %>%
  ggplot(aes(x = term, y = estimate, 
             ymax = conf.high, 
             ymin = conf.low,
             col = model)) +
    geom_pointrange() +
    coord_flip() +
    geom_hline(yintercept = 0, linetype = "dotted", color = "red", size = 1)  +
    labs(y = "Estimate",
         x = "",
         col = "Model",
         title = "Likely to vote in 2020 election") +
    ggrepel::geom_text_repel(aes(label = round(estimate, 2))) +
    scale_colour_brewer(palette = "Set1") + theme(legend.position = "bottom")

ggsave(here("outputs", "vote2020_imputed.png"), width = 8, 
       height = 8)
```

### Sub

Only mixed model 

```{r}
model_outs_binded <- bind_rows(mutate(model.outs.high, group = "High"),
          mutate(model.outs.low, group = "Low and middle")          )

model_outs_binded %>%
  filter(!str_detect(term, "(Intercept)|sd")) %>%
  mutate(term = recode(term, 
                       "usborn" = "Born in US",
                       "male" = "Male",
                       "gendiscrim" = "General discrimination",
                       "apa.discrim.rona" = "COVID discrimination",
                       "edu" = "Education",
                       "factor(wave)3" = "Wave 3",
                       "GOP" = "Republican",
                       "DEM" = "Democrat",
                       "age" = "Age")) %>%
  ggplot(aes(x = term, y = estimate, 
             ymax = conf.high, 
             ymin = conf.low,
             col = model)) +
    geom_pointrange() +
    coord_flip() +
    facet_wrap(~factor(group)) +
    geom_hline(yintercept = 0, linetype = "dotted", color = "red", size = 1)  +
    labs(y = "Estimate",
         x = "",
         title = "Likely to vote in 2020 election",
         col = "Group") +
    ggrepel::geom_text_repel(aes(label = round(estimate, 2))) +
    theme(legend.position = "bottom")

ggsave(here("outputs", "vote2020_sub_imputed.png"), width = 8, 
       height = 8)
```

## Biden candidacy

### Main 

```{r}
model.outs <- cal_glm(df)
```

```{r}
model.outs %>%
  filter(str_detect(model, "Within estimator")) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  ggplot(aes(x = term, y = estimate, 
             ymax = conf.high, 
             ymin = conf.low)) +
    geom_pointrange() +
    coord_flip() +
    geom_hline(yintercept = 0, linetype = "dotted", color = "red", size = 1) +
    ggrepel::geom_text_repel(aes(label = round(estimate, 2))) +
    labs(y = "Estimate",
         x = "",
         title = "Suppporting Democratic Presidential candidate") +
    theme(legend.position = "bottom")

ggsave(here("outputs", "biden_imputed.png"))
```

### Sub

```{r}
glm_outs_binded <- bind_rows(
mutate(cal_glm(df %>% filter(prior != 1)), group = "High"), 
mutate(cal_glm(df %>% filter(prior == 1)), group = "Low and Middle"))

glm_outs_binded %>%
  filter(str_detect(model, "Within estimator")) %>%
  filter(!str_detect(term, "(Intercept)")) %>%
  ggplot(aes(x = term, y = estimate, 
             ymax = conf.high, 
             ymin = conf.low)) +
    geom_pointrange() +
    coord_flip() +
    geom_hline(yintercept = 0, linetype = "dotted", color = "red", size = 1) +
    ggrepel::geom_text_repel(aes(label = round(estimate, 2))) +
    facet_wrap(~group) +
    labs(y = "Estimate",
         x = "",
         title = "Suppporting Democratic Presidential candidate")

ggsave(here("outputs", "biden_sub_imputed.png"), width = 10, 
       height = 10)
```